Enforced Invariant Confluence

### 2020-01-13 doc/the_vldb_journal_paper/sections/invariant_confluence.tex
Added definition equivalence proof.
Added proof that our definition of invariant confluence is the same as
Bailis' initial definition. Also started a list of changes that we'll
ultimately have to report to the reviewers.

>>>>

\subsection{Equivalence to Existing Definition}
Our definition of invariant confluence is different than the original
definition given in~\cite{bailis2014coordination}, but the difference is merely
cosmetic. We now prove that the two definitions are equivalent.

We say an expression $e$ \defword{recursively satisfies $I$}, denoted
$\Irec{e}$, if $e$ and all of $e$'s children satisfy $I$. That is,
\begin{itemize}
  \item
    $\Irec{s}$ if $I(s)$,

  \item
    $\Irec{t(e)}$ if $\Irec{e}$ and $I(t(e))$, and

  \item
    $\Irec{e_1 \join e_2}$ if $\Irec{e_1}$, $\Irec{e_2}$, and $I(e_1 \join
    e_2)$.
\end{itemize}

In~\cite{bailis2014coordination}, Bailis et al.\ define \sTIconfluence{} to
mean that (a) the start state $s_0$ satisfies the invariant and (b) all
\sTIreachable{} expressions recursively satisfying $I$ are closed under join.
That is, $O$ is \sTIconfluent{} if $I(s_0)$ and
\begin{gather*}
  \hspace{0.75in} \forall e_1, e_2 \in \setst{e}{\sTIreachablepredicate{e}}.\; \\
  \hspace{0.75in} \Irec{e_1} \land \Irec{e_2} \implies I(e_1 \join e_2)
\end{gather*}

\begin{theorem}\thmlabel{TwoIconfluenceDefs}
  Consider a state based object $O = (S, \join)$, a start state $s_0$, a set of
  transactions $T$, and an invariant $I$. The following two are equivalent:
  \begin{enumerate}
    \item
      $\setst{s \in S}{\sTIreachablepredicate{s}} \subseteq I$

    \item
      $I(s_0)$ and
      $\forall e_1, e_2 \in \setst{e}{\sTIreachablepredicate{e}}.\;
         \Irec{e_1} \land \Irec{e_2} \implies I(e_1 \join e_2)$
  \end{enumerate}
\end{theorem}
\begin{proof}
  First, we show that (1) implies (2). Trivially,
  $\sTIreachablepredicate{s_0}$, so by (1), $I(s_0)$. Let $e_1$ and $e_2$ be
  arbitrary \sTIreachable{} expressions. Then $e_1 \join e_2$ is also
  reachable, so by (1), $I(e_1 \join e_2)$.

  Next, we show that (2) implies (1). We prove by structural induction that for
  all $e$, $\sTIreachablepredicate{e} \implies \Irec{e}$. From this, (1) is
  immediate.
  \begin{itemize}
    \item \textbf{Case $s_0$.}
      $I(s_0)$ by (2), so $\Irec{s_0}$

    \item \textbf{Case $t(e)$.}
      Let $t(e)$ be \sTIreachable{}. Then, $\sTIreachablepredicate{e}$ and
      $I(t(e))$. By the inductive hypothesis, $\Irec{e}$, so by the definition
      of $\Irec{\cdot}$, $\Irec{t(e)}$.

    \item \textbf{Case $e_1 \join e_2$.}
      Let $e_1 \join e_2$ be \sTIreachable{}. Then,
      $\sTIreachablepredicate{e_1}$ and $\sTIreachablepredicate{e_2}$. By the
      inductive hypothesis, $\Irec{e_1}$ and $\Irec{e_2}$. By $(2)$, $I(e_1
      \join e_2)$. Thus, by the definition of $\Irec{\cdot}$, $\Irec{e_1 \join
      e_2}$.
  \end{itemize}
\end{proof}
